Error propagation error

### 2021-08-04 doc/method_validation/method_validation.Rmd
Add results comparison

---
title: "Error propagation error"
output: html_notebook
---

@@

```{r}
library(tidyverse)
library(hgis)
library(readxl)
library(here)
library(errors)
```

Load results from R data reduction
```{r}
results <- readRDS(here("data_analysed/carb_all.Rdata"))
df <- map_dfr(results[10], 2)
View(df)
```

Load MR's results. I think we'd have to grab individual cells to do this.

```{r}
dfm <- read_excel(here("doc/method_validation/HGIS\ Results.xlsx"))
```

@@

```{r}
summarize(stds, ratio_std = mean(corr_14_12),
            sig_ratio_std = sqrt(sum(max_err^2))/n())
```

@@

df <- df %>% 
  mutate(corr_14_12_err = set_errors(corr_14_12, max_err),
         norm_ratio_err = norm_gas(corr_14_12_err, ratio_std, fm_std))

df %>% select(pos, sample_name, norm_ratio, sig_norm_ratio, norm_ratio_err)

@@

>>>>

---
title: "Error propagation error"
output:
  html_document:
    df_print: paged
---

@@

```{r}
library(tidyverse)
library(hgis)
library(readxl)
library(here)
library(errors)
library(janitor)
```

Load results from R data reduction
```{r}
results <- readRDS(here("data_analysed/carb_all.Rdata"))
df <- map_dfr(results[10], 2)
```

Load MR's results.

```{r}
dfm <- read_excel(here("doc/method_validation/HGIS\ Results.xlsx"), skip = 2) %>% 
  select(pos = Pos, sample_name = `Sample Name`, sample_type = Type, 
         norm_ratio = Fm...5, sig_norm_ratio = dFm...6,
         fm_corr = Fm...11, sig_fm_corr = dFm...12) %>% 
  remove_empty("rows")
```

@@

```{r}
summarize(stds, ratio_std = mean(corr_14_12),
            sig_ratio_std = sqrt(sum(max_err^2))/n(),
          se_ratio_std = amstools::se(corr_14_12))
```

@@

dfe <- df %>% 
  mutate(corr_14_12_err = set_errors(corr_14_12, max_err),
         norm_ratio_err = norm_gas(corr_14_12_err, ratio_std, fm_std))

dfe %>% select(pos, sample_name, norm_ratio, sig_norm_ratio, norm_ratio_err)

@@

# Compare data

Compare data after applying new normalizing standard error propagation...

### Norm Ratio

```{r}
df %>% 
  select(pos, sample_name, norm_ratio, sig_norm_ratio) %>% 
  inner_join(select(dfm, pos, norm_ratio, sig_norm_ratio), by = "pos", suffix = c(".bl", ".mr")) %>% 
  mutate(norm_ratio_diff = norm_ratio.bl - norm_ratio.mr,
         sig_norm_ratio_diff = sig_norm_ratio.bl - sig_norm_ratio.mr)
```

### Blank corrected Fm

```{r}
df %>% 
  select(pos, sample_name, fm_corr, sig_fm_corr) %>% 
  inner_join(select(dfm, pos, fm_corr, sig_fm_corr), by = "pos", suffix = c(".bl", ".mr")) %>% 
  mutate(fm_diff = fm_corr.bl - fm_corr.mr,
         sig_fm_diff = sig_fm_corr.bl - sig_fm_corr.mr)
```
